\documentclass[12pt]{article}

\pagenumbering{gobble}
\usepackage{mypython, mymath}

\usepackage[margin=0.6in]{geometry}

\begin{document}
\begin{center}
   \LARGE Lecture 13
\end{center}

\section{Files}

In every project:

\begin{itemize}
   \item \lstinline{python3 skater.py < in_file > out}
   \item \lstinline{python3 moonlander.py < in_file > out}
   \item \lstinline{python3 solver.py < in_file > out}
\end{itemize}

Here, the reading from and writing to files was handled by the terminal itself,
not Python.  But what if I want to open a file and read from it from inside
Python?  We can!

\subsection{Reading Files}

\lstinputlisting{read_file.py}

\noindent
Draw picture with cursor, then modify to for loop!

\lstinputlisting{read_file2.py}

\subsection{Writing to Files}

What about writing to a file?  We can do that too!

\lstinputlisting{files.py}

\section{Sorting}

\subsection{Sorting Numbers}

\lstinputlisting{sorting.py}

\noindent
That's great!  We can use this to sort a list of anything\dots almost.  What if
I want to sort a list of objects?  How do I say what to sort based on?  What
if, for example, I wanted to sort a list of Pets.

\subsection{Sorting Pets}

\lstinputlisting{pets.py}

\section{Exceptions (Time Permitting)}

What happens when I do the following?

\lstinputlisting{get_num.py}

\noindent
To ask a slightly different question, what could go wrong?  What if I type in
``five''?  What happens then?

It crashes!  More specifically, it raises an exception!  More specifically, it
raises a \lstinline{ValueError} (this will be important in a moment).  But what
if I don't want the program to crash just because of a slight error?  I can
tell python to `try' to do something and do something else of an exception is
raised.

\lstinputlisting{get_num2.py}

\noindent
Let's modify the code so that I keep asking for a value until it's an integer.

\lstinputlisting{get_num3.py}

\noindent
Here I'm saying to `try' to do a possibly unsafe operation, and if a
\lstinline{ValueError} occurs, instead do something else.

\section*{Project 5}

Intro Project 5

\end{document}
