\documentclass[12pt]{article}

\pagenumbering{gobble}
\usepackage{mypython, mymath}

\usepackage[margin=0.6in]{geometry}

\begin{document}
\begin{center}
   \LARGE Lecture 16
\end{center}

\section*{Queries}

\textbf{In later section, remember to talk about \lstinline{raise}!!!}

\section{Sorting}

Both sections described selection sort, so we're going with that!
\[[25,\ 13,\ -100,\ -12,\ 60,\ 31,\ -76,\ 2]\]

\begin{itemize}
   \item Find the minimum (select it), swap with index 0
   \item Repeat for spots \(1,\ 2,\ \dots,\ n-1\)
\end{itemize}

\noindent
Go through example above; write out code.

\lstinputlisting{sel_sort.py}

\section{PPM}

Let's learn about ppm files!  Specifically the P3 format of ppm files!  The ppm
P3 format is a plain text format for storing images.  Let's take a look at
making an image!

\newpage

\begin{lstlisting}
P3
3 1
255
255 0 0 # red
0 255 0 # green
0 0 255 # blue
\end{lstlisting}

\noindent
Now let's make one that's a little bigger!

\begin{lstlisting}
P3
3 2
255
255 0 0   # red
0 255 0   # green
0 0 255   # blue
255 255 0 # yellow
255 0 255 # magenta
0 255 255 # cyan
\end{lstlisting}

\noindent
Mess with components per line, show them that it makes no difference/they'll
need to be able to handle it.  Then intro Program 6.

\section*{Truth Tables!}

Start simple: \(p\ \text{or}\ q\)

\noindent
Get harder: \(\text{not}\ ((\text{not}\ p\ \text{or}\ q)\ \text{and}\
(\text{not}\ q\ \text{or}\ r))\ \text{or}\ (\text{not}\ p\ \text{or}\ r)\)

\section*{Methods?}

\section*{Git?}

\section*{Insertion Sort?}

\begin{itemize}
   \item Start at index 1, swap with lower one until it gets to the correct
      location (insert it).
   \item Each iteration, the first \(i\) elements of the list are sorted, each
      subsequent element is then inserted.
\end{itemize}

Go through example above.  Write out code?

\lstinputlisting{ins_sort.py}

\end{document}
